Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-24 doc/JFLA2022/paper.tex
Coq users are forever learners.

We call on the Coq users in the JFLA community and beyond to come and join us in this effort, by bringing new interesting projects which are worth presenting to Coq learners and guiding them in their exploration.
%
We also always have project ideas to extend further our explorations and anyone is welcome to join the team by sending small or larger contributions through pull requests.
%
The current state of the project is already the result of such evolutions after several of us contributed project solutions and new proposals to the initial version of the first author.

>>>>

We call on the Coq users in the JFLA community and beyond to come and join us in this effort, by bringing new interesting projects which are worth presenting to Coq learners, \emph{a.k.a.} Coq users, and guiding them in their exploration.
%
We also always have project ideas to extend further our explorations and anyone is welcome to join the team by sending small or larger contributions through pull requests.
%
The current state of the project is already the result of such evolutions after several of us contributed project solutions and new proposals to the initial version of the first author.
